Demo arXiv template

### 2022-10-05 paper/paper.qmd
notes after the meeting

@@

Index construction is a way to summarise complicated information (used in environmental data). 
The complexity of these information may involve a spatial distribution, a temporal scale that defines the frequency of the data, and a multivariate perspective that collects different climate variables.

@@

# Natural hazard indices

## Climate indices

## Drought indices

## Economics/ social indices

@@

@@

@@

Take one or multiple variables to create a new variable, linearly? 
sometimes called feature extraction in the machine learning community 
With drought indices, the extraction of meaningful variables from the original data is usually supported by the water balance model, for example, in SPEI, the step that create $d$ out of precipitation and potential evapotranspiration (PET) has theoretical backup from [see paper.]

@@

@@

# Extending the pipeline

@@

>>>>

* indices, why do we need them, decision making
* define what is an index, what is not even if they are called index
* only very brief on indices in the introduction
* potential audience + what do you think they should learn from this work.

@@

<!-- Index construction is a way to summarise complicated information (used in environmental data). **it basically says nothing** -->
The complexity of these information may involve a spatial distribution, a temporal scale that defines the frequency of the data, and a multivariate perspective that collects different climate variables.

@@

**Why index is useful, why people care about indices**

**review indices, climate, drought, economic, UN and other indices**

**What is the problem with current workflow on index construction**

**who would benefit from this paper: 1) people proposing new indices; 2) people analysing index variation, compare between indices, 3) those making decisions from indices, 4) other statistician, how to modularise steps for anlaysis in your domain.**

@@

**Another section on original data directly downloaded, can have different spatial resolution, temporal granularity, data quality problem. After processing them and align them together they become the "raw data"**

@@

mostly happen with raster data

## Scaling

standardising
close to variable transformation step

@@

<!-- Take one or multiple variables to create a new variable,  -->
Restrict it to single variable, square root, log etc could be linearly, also non-linear

GAM, can you do additive model pairwise/ three-way

@@

sometimes called feature extraction in the machine learning community 
With drought indices, the extraction of meaningful variables from the original data is usually supported by the water balance model, for example, in SPEI, the step that create $d$ out of precipitation and potential evapotranspiration (PET) has theoretical backup from [see paper.]

@@

# Incorporating new methods into the pipeline

<!-- # [Extending the pipeline] a different name here: alternate a module with a different (method) -->

@@

## Calculating SPEI with raster data

### 2022-10-05 paper/paper.tex
notes after the meeting

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, borderline west={3pt}{0pt}{shadecolor}, breakable, sharp corners, boxrule=0pt, interior hidden, frame hidden]}{\end{tcolorbox}}\fi

@@

Index construction is a way to summarise complicated information (used
in environmental data). The complexity of these information may involve
a spatial distribution, a temporal scale that defines the frequency of
the data, and a multivariate perspective that collects different climate
variables.

@@

\hypertarget{natural-hazard-indices}{%
\section{Natural hazard indices}\label{natural-hazard-indices}}

\hypertarget{climate-indices}{%
\subsection{Climate indices}\label{climate-indices}}

\hypertarget{drought-indices}{%
\subsection{Drought indices}\label{drought-indices}}

\hypertarget{economics-social-indices}{%
\subsection{Economics/ social indices}\label{economics-social-indices}}

@@

@@

@@

Take one or multiple variables to create a new variable, linearly?
sometimes called feature extraction in the machine learning community
With drought indices, the extraction of meaningful variables from the
original data is usually supported by the water balance model, for
example, in SPEI, the step that create \(d\) out of precipitation and
potential evapotranspiration (PET) has theoretical backup from {[}see
paper.{]}

@@

@@

\hypertarget{extending-the-pipeline}{%
\section{Extending the pipeline}\label{extending-the-pipeline}}

@@

>>>>

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, borderline west={3pt}{0pt}{shadecolor}, frame hidden, interior hidden, boxrule=0pt, sharp corners, breakable]}{\end{tcolorbox}}\fi

\begin{itemize}
\tightlist
\item
  indices, why do we need them, decision making
\item
  define what is an index, what is not even if they are called index
\item
  only very brief on indices in the introduction
\item
  potential audience + what do you think they should learn from this
  work.
\end{itemize}

@@

The complexity of these information may involve a spatial distribution,
a temporal scale that defines the frequency of the data, and a
multivariate perspective that collects different climate variables.

@@

\textbf{Why index is useful, why people care about indices}

\textbf{review indices, climate, drought, economic, UN and other
indices}

\textbf{What is the problem with current workflow on index construction}

\textbf{who would benefit from this paper: 1) people proposing new
indices; 2) people analysing index variation, compare between indices,
3) those making decisions from indices, 4) other statistician, how to
modularise steps for anlaysis in your domain.}

@@

\textbf{Another section on original data directly downloaded, can have
different spatial resolution, temporal granularity, data quality
problem. After processing them and align them together they become the
``raw data''}

@@

mostly happen with raster data

\hypertarget{scaling}{%
\subsection{Scaling}\label{scaling}}

standardising close to variable transformation step

@@

Restrict it to single variable, square root, log etc could be linearly,
also non-linear

GAM, can you do additive model pairwise/ three-way

@@

sometimes called feature extraction in the machine learning community
With drought indices, the extraction of meaningful variables from the
original data is usually supported by the water balance model, for
example, in SPEI, the step that create \(d\) out of precipitation and
potential evapotranspiration (PET) has theoretical backup from {[}see
paper.{]}

@@

\hypertarget{incorporating-new-methods-into-the-pipeline}{%
\section{Incorporating new methods into the
pipeline}\label{incorporating-new-methods-into-the-pipeline}}

@@

\hypertarget{calculating-spei-with-raster-data}{%
\subsection{Calculating SPEI with raster
data}\label{calculating-spei-with-raster-data}}
